Field-informed Reinforcement Learning for Learning Large-Scale Collective Tasks

### 2023-05-16 paper.tex
more comments

\subsection{Scenario}
The proposed simulation consists 
 of a set of robots placed in a 2D space capable of perceiving the intensity 
 of the phenomenon of interest through an installed sensor $\zeta_v$ with $v \in \mathbb{V}$. 
 (e.g., camera, temperature sensor, etc.). 
%
Additionally, each node has a coverage range $\omega$ 
 that describes the area it can monitor. 
 Each drone can only communicate directly with its own neighbourhood $\mathcal{N}$, 
 which in this case depends on a $\mathbb{O}$ range,
From the neighbourhood, 
 each node can also perceive the direction of the other nodes.
%
Each node moves following a certain action composed of two components ($\alpha$, $\theta$) 
 which respectively describe the angle and intensity of the movement (i.e., the velocity vector).
 \lukas{drone, robot, agent, node...}
\subsection{Goal}
 The objective of this scenario is to:
\begin{itemize}
\item Maximise the number of drones within the phenomena
\item Minimise the number of drones without a neighbourhood
\item Maximise the coverage of the system
\end{itemize}

@@

 Regarding the first point, the reward function is simple and is defined as:

 \begin{equation*}
 R^a_{v} = \begin{cases}
  1 & \text{if } \zeta_v > 0 \\
  0 & \text{otherwise} 
 \end{cases}
 \end{equation*}

This will lead the system to prefer a configuration in which every node is present in the system. 
%
The second point is important because if the system breaks into many scattered drones, 
 they are not able to move in the environment due to the reduced observability of the system. 
 In this case, the reward is defined as:

 \begin{equation*}
 R^{\mathcal{N}}_{v} = \begin{cases}
  1 & \text{if } \mathcal{N} > 0 \\
  0 & \text{otherwise} 
 \end{cases}
 \end{equation*}

 Finally, to maximise the coverage, 
  we decided to calculate the maximum and minimum distance of the neighbourhood and give more value in case these two values are similar. 
%
This means that the average distance will tend towards the one expressed by the viewing range of each node:
% 
\begin{equation*}
R^{C}_{v} = \frac{d_{max} - d_{min}}{\mathbb{O}}
\end{equation*}
The final reward function is defined as:
\begin{equation*}
R_{v} = \frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}
\end{equation*}
Specifically, we decided to express the signal as a \emph{regret}
  as it is a more general measure of the quality of the action taken by the agent.
It is simplify evaluated as:
\begin{equation*}
R^e_{v} = R_v - 1
\end{equation*}
%

>>>>

\subsection{Scenario}
The proposed simulation consists 
 of a set of robots placed in a 2D space capable of perceiving the intensity 
 of the phenomenon of interest through an installed sensor $\zeta_v$ with $v \in \mathbb{V}$. 
 (e.g., camera, temperature sensor, etc.). 
%
Additionally, each node has a coverage range $\omega$ 
 that describes the area it can monitor. 
 Each drone can only communicate directly with its own neighbourhood $\mathcal{N}$, 
 which in this case depends on a $\mathbb{O}$ range. \lukas{$\mathbb{O}$  not defined.}
From the neighbourhood, 
 each node can also perceive the direction of the other nodes.
%
Each node moves following a certain action composed of two components ($\alpha$, $\theta$) 
 which respectively describe the angle and intensity of the movement (i.e., the velocity vector).
 \lukas{drone, robot, agent, node...}
\subsection{Goal}
 The objective of this scenario is threefold:
\begin{enumerate}
\item Maximise the number of drones within the phenomena ($ndp$)
\item Minimise the number of drones without a neighbourhood
\item Maximise the coverage of the system
\end{enumerate}

@@

% Regarding the first point, the reward function is simple and is defined as:
Formally, we define the reward of a drone being within the phenomena as
 \begin{equation*}
 R^a_{v} = \begin{cases}
  1 & \text{if } \zeta_v > 0 \\
  0 & \text{otherwise.} 
 \end{cases}
 \end{equation*}

 I.e., a drone is considered within the phenomena as soon as the drone can sense the phenomenon.
This will lead the system to prefer a configuration in which every node is present in the system. \lukas{do you mean `... is present within the phenomenon'?}
%
The second element in the objective function ensures cohesion among the agents. This is important because if the system breaks into many scattered drones, the observability of the phenomenon is reduced, limiting the ability of the agents to move appropriately in the environment.
% they are not able to move in the environment due to the reduced observability of the system. 
 In this case, the reward is defined as:
 \begin{equation*}
 R^{\mathcal{N}}_{v} = \begin{cases}
  1 & \text{if } \mathcal{N} > 0 \\
  0 & \text{otherwise} 
 \end{cases}
 \end{equation*}

 Finally, to maximise the coverage, 
  we decided to calculate the maximum and minimum distance of the neighbourhood and give more value in case these two values are similar. \lukas{minimum / maximum distance to what? the next neighbour? measuring the phenomena?}
%
This means that the average distance will tend towards the one expressed by the viewing range of each node:
% 
\begin{equation*}
R^{C}_{v} = \frac{d_{max} - d_{min}}{\mathbb{O}}
\end{equation*}
where 
$d_{max}$ and $d_{min}$ describes the maximum and minimum distance of the node to \lukas{??}, respectively. This distance is normalized by the maximum communication range of each agent $\mathbb{O}$.
\lukas{should this be $1-R^C_v$? or do we want to favour the highest average distance?}
The final reward function for an agent $v$ is defined as:
\begin{equation*}
R_{v} = \frac{R^a_{v} + R^{\mathcal{N}}_{v} + R^{C}_{v}}{3}
\end{equation*}
Specifically, we decided to express the signal as a \emph{regret}
  as it is a more general measure of the quality of the action taken by the agent.
It is simplify evaluated as:
\begin{equation*}
R^e_{v} = R_v - 1
\end{equation*}
%
